Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-01-06 supplement.tex
edits to relate discussion

We used \Relate \citep{Speidel2019-nj} to reconstruct gene genealogies from the
simulations under our four inferred demographic models. From each of these,
following the same approach as for the analysis of the actual data, we computed
coalescence rates within and between sampled populations. From the coalescence
rates, we estimated the inverse instantaneous coalescence rate (IICR, often
interpreted as a trajector of $N_e$) for each population, as well as relative
cross coalescence rates between pairs of populations.

We note that the IICR is a function of not only population sizes, but also of
population structure and migration, and interpreting it as an actual population
size history is tenuous.  However, it is still a statistic that can be computed
from the data and compared to predictions under the model, and can therefore be
informative about aspects of the data that our models fail to predict.
\aprcomment{I think we want to say something along these lines above\dots} We
also note that the coalescence rates inferred from data used a larger set of
populations from the combined 1000 Genomes/AGRP dataset, while our model
simulations only included a subset of 5 populations. This may lead to
differences in resolution of the inferences.

>>>>

We used \Relate \citep{Speidel2019-nj} to reconstruct gene genealogies from the
simulations under our four inferred demographic models. From each of these,
following the same approach as for the analysis of the actual data, we computed
coalescence rates within and between sampled populations. From the coalescence
rates, we estimated the inverse instantaneous coalescence rate (IICR, often
interpreted as an estimator of $N_e$) for each population, as well as relative
cross coalescence rates between pairs of populations.

The IICR is only a reliable estimator of $N_e$ in the absence of population structure. . However, since IIRC are readily estimated and visually interesting, it is commonly attempted even when the assumption is not met \cite{}. 
Even if the assumption is not met, the inferred IIRC can be interpreted as a summary statistic for which model predictions can be compared to data. and can therefore be
informative about aspects of the data that our models fail to predict.
\sgcomment{Insert inferences with same populations?}. We
also note that the coalescence rates inferred from data used a larger set of
populations from the combined 1000 Genomes/AGRP dataset, while our model
simulations only included a subset of 5 populations. This may lead to
differences in resolution of the inferences.
